On Optimality of Finite Element Integration

### 2015-10-18 TOMS_Paper/assembly.tex
Trying to rewrite algorithm...

\begin{figure}
\begin{lstlisting}[numbers=left, basicstyle=\small\ttfamily, frame=single]
M = $\lbrace$m | m is a monomial in the input expression$\rbrace$
S = $\lbrace$m | $\theta(m)$ < 0$\rbrace$
P = $\lbrace$m | $\theta(m)$ $\geq$ 0 and sharing(m, S) = $\emptyset \rbrace$
maybe_P = M $\setminus$ (S $\cup$ P)
B = $\lbrace$b | b is a bipartite graph from complete graph G = (maybe_P, E)$\rbrace$
for each $b \in B$:
  for each $(b_S, b_P) \in b$:

for each expression:
  remove sharing    
\end{lstlisting}
\caption{High level view of the transformation algorithm}
\label{code:intuition}
\end{figure}

If pre-evaluation is found profitable (i.e., $\theta(m) > 0$), the sub-expression implementing $m$ is extracted; the surrounding loop nest is suitably ``cloned''; a sequence of transformation steps -- involving expansion, factorization, and code motion -- takes place (details in Section~\ref{sec:codegen}); and, finally, the hoisted code is pre-evaluated using symbolic execution. The result is a set of $n$-dimensional tables (these can be seen as ``slices'' of the reference tensor at the math level), $n$ being the arity of the multilinear form.

>>>>

\begin{figure}
\begin{lstlisting}[numbers=left, basicstyle=\small\ttfamily, frame=single]
M = $\lbrace$m | m is a monomial in the input expression$\rbrace$
S = $\lbrace$m | $\theta(m)$ < 0$\rbrace$
maybe_P = M $\setminus$ S
B = $\lbrace$b | b is a bipartite graph from complete graph G = (maybe_P, E)$\rbrace$
for each $b \in B$:
  for each $(b_S, b_P) \in b$:
    if memory_required($b_P$) $\geq$ $T_H $:
      continue
    op_count[b] = \eta(S $\cup$ b_S) + $|\theta(b_P)|$
for each expression:
  remove sharing
\end{lstlisting}
\caption{High level view of the transformation algorithm}
\label{code:intuition}
\end{figure}

%If pre-evaluation is found profitable (i.e., $\theta(m) > 0$), the sub-expression implementing $m$ is extracted; the surrounding loop nest is suitably ``cloned''; a sequence of transformation steps -- involving expansion, factorization, and code motion -- takes place (details in Section~\ref{sec:codegen}); and, finally, the hoisted code is pre-evaluated using symbolic execution. The result is a set of $n$-dimensional tables (these can be seen as ``slices'' of the reference tensor at the math level), $n$ being the arity of the multilinear form.
